Wheels of Misfortune: Exploring Auto Theft Trends in Ottawa

### 2024-04-25 paper/paper.qmd
updated paper, references

@@

The dataset used for this paper was provided by Ottawa Police [@citeOttawa]. The dataset contains theft of motor vehicle occurrencesfrom the years 2018-2023.The data was cleaned by using the open source statistical programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `kableExtra` [@kableExtra], `janitor` [@janitor], arrow [@arrow] ,and `knitr` [@knitr].

>>>>

The paper uses the data provided by Ottawa Police [@citeOttawa]. The dataset defines auto theft as the act of taking or another person's vehicle [@citeOttawa].The data was cleaned by using the open source statistical programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `kableExtra` [@kableExtra], `janitor` [@janitor], arrow [@arrow] ,and `knitr` [@knitr].

@@

The dataset provided by Ottawa Police contains all theft of motor vehicle occurrences from the years 2018-2023. The data is updated annually, and is available for public use.
